%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Masters of Structural Engineering (Structural Mechanics) \emph{cum laude}} % Degree
    {Delft University of Technology} % Institution
    {Delft, The Netherlands} % Location
    {Sep. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Placed first in the following courses: Timber and Timber Structures 1, Steel Structures 2, Probabilistic Design, Plastic Analysis, Structural Dynamics, Stability of Structures, Prestressed Concrete, Computational Modelling of Structures.}
        \item {Graduation Thesis titled `\href{https://repository.tudelft.nl/islandora/object/uuid\%3A86d469f3-0c44-4f45-9396-ec296d87031f?collection=education}{A Multiphysics Numerical Framework for Epoxy Resins}' awarded a 9/10.}
        \item {Overall Weighted Average: 9.1/10.}
        \item {Delft University of Technology was ranked 4\textsuperscript{th} in the QS World University Rankings for Civil/Structural Engineering in 2018.}
      \end{cvitems}
    }
    \cventry
    {Bachelor of Civil Engineering (Structures) (Hons. I)} % Degree
    {The University of Sydney} % Institution
    {Sydney, Australia} % Location
    {Mar. 2009 - Nov. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {High distinction average, with a thesis investigating the crosswind loading and vortex shedding of a building with a unique profile that was inspired by the tubercles on a humpback whale's fin.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
