%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Design Engineer} % Job title
    {Partridge Structural} % Organization
    {Sydney, Australia} % Location
    {Dec. 2011 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Partridge is a medium sized consulting firm that practices in a range of disciplines and specialises in high-end residential projects. In my role as design engineer I was responsible for the detailed structural design and documentation of a variety of building projects including residential, multi-residential, event, commercial and public works.}
        \item {The following list of projects gives an indication of the structural analysis and design that I have carried out during my time at Partridge.}\\
        \textbf{Unconventional Structures:}
          \begin{itemize}
            \item \emph{SkyMate I:} Design of a 26 metre high steel cable structure for use as an aerial adventure park. A 3D frame model was used to validate the redundancy of the cable structure and the impact of varying cable sag. A non-linear finite element analysis was performed for a critical structural connection to determine its plastic capacity. This project was the joint winner of the Association of Consulting Structural Engineers NSW: Special/Unusual Projects category in 2016.
            \item \emph{SkyMate II:} An evolution of SkyMate I incorporating similar design aspects to suit a narrow and difficult site. A new lateral stability system was devised to suit the new design. A 30 m long zip line with a cantilevered exit tower was integrated into the structure.
            \item \emph{Samsung Spiral Stairs:} Design of a 14 metre steel plate spiral staircase for an office fit-out. A harmonic analysis was conducted to verify that the human-induced vibration of the stairs was within acceptable limits.
            \item \emph{Woodford Cable Net:} Analysis of a 20 metre triangular grid of steel cables that formed a netted shade structure over a performance space. A construction sequence analysis of the cable net was performed to determine the optimal drape of the cables.
            \item \emph{Sydney Wild Life Zoo – Wild Flight:} Design of a 60 m long aerial ride, suspended by a complex array of cables from an existing arched roof structure. The existing roof spanned 40 metres with a shallow arch profile and had limited reserve capacity. A non-linear analysis was performed to confirm its adequacy and necessary strengthening measures were designed and incorporated into the new structure.
          \end{itemize}
          \textbf{Residential Structures:}
          \begin{itemize}
            \item \emph{105 Ramsgate Avenue:} Analysis of a five-storey residential concrete
            framed building with multiple transfer levels, featuring slender columns below the lower transfer level. A VBA program was developed to ensure concrete filled steel columns had sufficient strength and stability.
            \item \emph{58 John Street:} Design and detailing of a three-storey residential building using mixed construction. Staged shoring was required to allow excavation into sand and rock adjacent to the neighbouring properties. A bespoke steel stair, with a structural plate balustrade was designed to be suspended from a perforated steel plate spine.
            \item \emph{7 Wolseley Crescent:} Alterations and additions of an existing waterfront property that involved significant demolition and temporary propping. Two stories of concrete were supported on a grid of heavy steelwork with 7 metre long props as the two levels underneath were demolished and rebuilt. Extensive strengthening of the existing structure was required to achieve the new architectural brief.
            \item \emph{15 Beaconsfield Road:} Design and detailing of a four-storey residential building with large cantilevered balconies and a concrete wall acting as a deep beam.
          \end{itemize}
          \textbf{Multi-Residential Structures/Public Works:}
          \begin{itemize}
            \item \emph{Hudson Street:} Design of a six-storey concrete framed multi-residential
            building. Strut and tie analyses were used to confirm the adequacy of
            concrete walls acting as deep beam transfer elements.
            \item \emph{Sydney Light Rail Extension:} Design of cantilevered steel awnings and
            associated platform infrastructure for the Inner West Light Rail Extension.
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University Tutor} % Job title
    {The University of Sydney} % Organization
    {Sydney, Australia} % Location
    {Jul. 2010 - Jun. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was a tutor for the second year subject CIVL2201: Structural Mechanics, and the first year subject ENGG1061: Advanced Engineering.}
        \item {As a tutor for CIVL2201 I was required to deliver a two hour tutorial to thirty students each week, in which I reinforced the coursework delivered in the lectures and assisted with tutorial questions and assignments.} 
        \item {As a tutor for ENGG1061 I mentored six advanced engineering students by helping them to deliver a creative solution to an engineering problem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Research Scholar} % Job title
    {The University of Sydney} % Organization
    {Sydney, Australia} % Location
    {Dec. 2010 - Mar. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was awarded a scholarship to conduct research in a field of my choosing under the supervision of an academic in the School of Civil Engineering.} 
        \item {In my research, titled ‘Validation of the Cobra Probe’, I devised a unique method for the calibration of the Cobra Probe anemometer.} 
        \item {Following an extensive literature review I developed a LabVIEW calibration program, which facilitated the integration of the probe into the wind tunnel at the School of Civil Engineering.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
