%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Design Engineer} % Job title
    {Partridge Structural} % Organization
    {Sydney, Australia} % Location
    {Dec. 2011 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Partridge is a medium sized consulting firm that practices in a range of disciplines and specialises in high-end residential projects. In my role as design engineer I was responsible for the detailed structural design and documentation of a variety of building projects including residential, multi-residential, event, commercial and public works.}
        \item {I have experience in the structural analysis and design of projects in the following sectors:}
        \begin{itemize}
          \item Unusual Structures
          \item Residential Structures
          \item Multi-Residential Structures
          \item Public Infrastructure
        \end{itemize}
        \item A portfolio showcasing a selection of my structural design work is available at \href{https://robbievanleeuwen.github.io}{https://robbievanleeuwen.github.io}.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University Tutor} % Job title
    {The University of Sydney} % Organization
    {Sydney, Australia} % Location
    {Jul. 2010 - Jun. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was a tutor for the second year subject CIVL2201: Structural Mechanics, and the first year subject ENGG1061: Advanced Engineering.}
        \item {As a tutor for CIVL2201 I was required to deliver a two hour tutorial to thirty students each week, in which I reinforced the coursework delivered in the lectures and assisted with tutorial questions and assignments.} 
        \item {As a tutor for ENGG1061 I mentored six advanced engineering students by helping them to deliver a creative solution to an engineering problem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Research Scholar} % Job title
    {The University of Sydney} % Organization
    {Sydney, Australia} % Location
    {Dec. 2010 - Mar. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was awarded a scholarship to conduct research in a field of my choosing under the supervision of an academic in the School of Civil Engineering.} 
        \item {In my research, titled ‘Validation of the Cobra Probe’, I devised a unique method for the calibration of the Cobra Probe anemometer.} 
        \item {Following an extensive literature review I developed a LabVIEW calibration program, which facilitated the integration of the probe into the wind tunnel at the School of Civil Engineering.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
